The problem and promise of scale in multilayer networks

### 2019-09-11 paper/introduction.Rmd
new refs.bib
fin skeleton
start intro

---
title: The problem and promise of scale in multilayer networks
output: 
  github_document:
    toc: true
author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
date: "-- `r Sys.Date()`"
bibliography: multilayer-networks.bib
---

>>>>

---
title: The problem and promise of scale in multilayer networks
output: 
  github_document:
    toc: true
author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
date: "-- `r Sys.Date()`"
bibliography: ../references/refs.bib
---

# Introduction

Animal social systems are complex and multifaceted

traditionally, animal social systems are measured using direct observation, telemetry or pit tags
interactions, e.g. grooming, aggression, etc,  between individuals are quantified by simplified measures 
and often lacking any indication of the spatial context of the interaction

recently the multilayer has been used to

along with spatial variables, comes a large history of landscape ecology exploring and evaluating sensitivity to scale

here we'll use simulations to evaluate the impact of scale on social and spatial variables 
to better understand it's impact, implications in ML networks

# Multilayer Networks

Multilayer networks combine multiple networks layers with interlayer edges

Layers in multilayer networks can be
Animal social systems are

What is a network

How does a ML network build on that

What kinds of ML nets exist

Which can include spatial variables

Multifaceted nature of animal social systems 
many variables having a spatial component
including landcover and habitat type
fix rate and

spatial variables defined by

# Scale
Scale

in grain and extent

grain is this

extent is this
